\section{Product Specification}

Within section \ref{sec:userrequirements} the user requirements as defined by 
BlackBerry were prioritised using the MoSCoW prioritisation system. In order to 
ensure that the final product is delivered to the expectation of the client, a
product specification will be proposed. 

The product specification below follows a similar layout to what was seen in 
section \ref{sec:userrequirements} (User Requirements). Prioritising the 
various objectives within the system, can help to ensure that the most 
important aspects of the system are developed first. It also highlights any 
potential issues that may occur.


\subsection{Must}
\begin{itemize}
  \item Parse any number of KML files (one or more) at any one time;
  \item Convert each Placemark found within each KML file to an Event;
  \item Cluster all the Events upon a weekly basis;
  \item Cluster all the Events upon a product basis;
  \item Highlight the overall differences of RAT usage between weeks and 
        products;
  \item Highlight the overall differences of Mix Band usage between weeks and 
        products;
  \item Highlight the overall differences of Start RRC State usage between 
        weeks and products;
  \item Highlight the inter-cluster differences of RAT usage between weeks and 
        products;
  \item Highlight the inter-cluster differences of Mix Band usage between weeks 
        and products;
  \item Highlight the inter-cluster differences of Start RRC State usage  
        between weeks and products.
\end{itemize}


\subsection{Should}
\begin{itemize}
  \item Visualise the differences of data to allow for easy comparison when 
        trying to compare upon a weekly basis;
  \item Visualise the differences of data to allow for easy comparison when 
        trying to compare upon a product basis;
  \item Produce an output KML file highlighting all clusters and events. Each
        cluster must visually show it's radius;
  \item Produce a heatmap to highlight the strong areas of event density.
\end{itemize}


\subsection{Could}
\begin{itemize}
  \item Allow the use to easily apply filters to the analysed data to help 
        further ``drill down'' into the analysis;
  \item Highlight the change in velocity differences along the test route.
\end{itemize}


\subsection{Won't}
\begin{itemize}
  \item Directly interact with any internal BlackBerry data sources.
\end{itemize}