\section*{Abstract}
The Mobile Network is a powerful series of interconnected fixed and mobile 
computer systems. Mobile devices that utilise the Mobile Network are now able 
to connect to the Mobile Network in many parts of the world. Mobile devices are 
now thought of as the centre of everyday life, becoming an essential modern day
tool.

The development of a mobile device is an ever increasingly complex task. In 
recent years a shift towards reducing the size of a device, improving battery 
it's life and increasing the processing power have all taken over some of the 
more fundamental issues of mobile device development --- efficiency and 
reliability.

This project will focus upon aiding BlackBerry Test Engineers to improve the 
reliability of mobile devices, when attempting to communicate with the mobile 
mobile network - whether that would be in terms of calls or data.

This project will classify, and analyse call data to try to help identify 
patterns of failed tests. By classifying data based upon similarities, it 
allows Test Engineers to be able to quickly and accurately identify problematic 
events. Once the problematic events have been fixed, patches to hardware or 
software can be rolled out to the end user, thus providing an improved final 
product to the customer.

\vfill
\thispagestyle{empty}

{
  \scriptsize

  BlackBerry\textsuperscript{\textregistered}, 
  RIM\textsuperscript{\textregistered}, 
  Research In Motion\textsuperscript{\textregistered} and related trademarks, 
  names and logos are the property of Research In Motion Limited and are 
  registered and/or used in the U.S. and countries around the world. 

  All other trademarks are the property of their respective owners.
}