\section{General Requirements}
The general requirements are ones that define the business policies, standards 
and needs \citep{cadle10}. Many of the requirements are not related to this 
project, but will be noted for reference purposes.

\subsection{Business constraints}
The business constraints are the constraints that will directly effect this 
project. There are no constraints from BlackBerry, however there are time based 
constraints from the University.

\subsection{Business policies}
The business policies cover aspects such as business standards and business 
policy decisions. These are enforced to ensure consistency across is maintained 
across an organisation. This project has no requirements to deal with business 
policies.

\subsection{Legal}
\subsubsection*{Copyright, Designs and Patents}

In order to avoid various patent disputes, any third party resources, such as 
programming languages, development tools and external libraries will be only 
used if the licence associated with the item is of a non-proprietary agreement.

However there are some circumstances where by proprietary sources will have to 
be used for example the use of Visual Studio 2010. 

These sources will have been chosen to meet the interests of all parties 
involved, and where applicable the version of software will be taken into 
consideration. 

Any use of non-proprietary software must first be accepted by BlackBerry, to 
ensure that the correct licences are used.

All software released by this project will be under the New BSD Licence (also 
referred to as the BSD 3-Clause License). This license allows for 
re-distribution and use in both source and binary formats. 

The license also allows for the source code to be modified as long as the 
licence agreements are met.

\subsubsection*{Data Protection}
The Data Protection Act (1998) provides security for personal or business data 
that is stored electronically. In order for the project to continue, there will 
be various pieces of data required to fully test the system from BlackBerry. 
The data is to be transmitted via an encrypted form, and will not be passed on 
to any third parties. 

All data is of the property of BlackBerry unless otherwise stated.

\subsubsection*{Intellectual Property}
All intellectual property rights will belong to BlackBerry, once the project 
has been assessed by the university. This will allow for future modification 
and extension to the end deliverable from this project. Once the project is 
completed, the licence agreement can be updated to reflect BlackBerry’s 
business practice if required.

\subsection{Branding}
The branding requirement is concerned with the image and style promoted by 
BlackBerry. This would take into considerations such as style guides, fonts and 
logos. 

The end product is intended for internal use only (not for public use), and 
hence the branding requirements will not need to be followed.

\subsection{Cultural}
This section is devoted to BlackBerry's culture, such as management styles. As 
the project is not being developed within BlackBerry's facilities, the culture 
style is not required to be taken into consideration.

\subsection{Language}
This project will be completed utilising the English (British) language. 
Additional languages will not be supported.