\section{Industry Reflection}
\label{sec:industry_reflection}

\begin{quote}
The Cluster Analysis Tool is a project executed by Luke as part of his final 
year project. The tool is an extension to an in-house project that was started
by Luke during his placement (Call Performance Analysis and Reporting System 
--- CPARS).

CPARS is able analyse various test routes and the results of the tests upon a 
large scale, however it is unable to provide analysis upon a geographical 
level.

The Cluster Analysis Tool is able to provide this level of geographical 
analysis as well as being able to automate the performance analysis activities 
within BlackBerry.

The tool has now been delivered to BlackBerry and meets many of the 
requirements that were initially defined. 
 
The tool allows BlackBerry to analyse the field performance of its devices by 
clustering events (drops and fails) that occur within a close geographical 
proximity of each other.

The tool produces valuable features, to which when integrated with CPARS, will
help test engineers to improve the analysis and understanding of these events. 

The tool has immense potential and it was only due to time constraints that 
caused certain requirements to be left out of delivery --- e.g. the ability to
detect differences of velocity between two data sets.
 
Our team is very impressed and grateful to Luke for the delivery of tool.
\end{quote}

\begin{flushright}
Anup Vijay \\
Call Performance Team Leader \\
Monday, 22$^n$$^d$ April 2013
\end{flushright}